Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-11-28 paper/tex/discussion.tex
add winnowing comment, few other fixes

\section{Discussion}
\label{sec:discussion}
%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, Eve Kovacs, Tony Tyson, Tina Peters)
In this paper we presented results evaluating the computation of individual galaxy photometric redshift PDFs for twelve photo-$z$ codes.  As discussed in Section~\ref{sec:metrics} the $p(z)$ should accurately reflect the relative likelihood as a function of redshift for each galaxy.  All codes were provided a set of representative training data and tested on an idealized set of model galaxies with high signal-to-noise and photometry with no confounding effects due to blending, instrumental effects, the night sky, or other complications included.  The goal was not to determine a ``best'' photo-$z$ code: in many ways, this was a baseline test of a ``best case scenario'' to predict the expected photo-$z$ performance if a stage IV dark energy survey was to obtain complete training samples and perfectly calibrated their multi-band photometry.  Given these idealized conditions, any deficiencies observed in a photo-$z$ code's performance should be a cause for concern, and may be evidence of a problem with either/both of the specific code implementation or the underlying algorithm.  In order to meet the stringent LSST goals for photo-$z$ performance, identifying and correcting such problems is an important first step before tackling more realistic data in future challenges.  Many of the codes tested performed well; however, several did not meet the stringent goals that have been laid out for LSST photometric redshift performance for individual galaxies, as laid out in the LSST SRD (See Section~\ref{sec:intro}.  This is a cause for concern, given the idealized conditions, and the individual code responses will be studied in detail moving forward.  If methods can not reach the goals on idealized data, then they will almost surely not meet those same goals when the more complex problems that we expect to arise from real LSST data are included.  The results presented in this paper enable an evaluation of which algorithms are the most promising moving forward, and potentially point to implementation choices or mistakes which could be improved or corrected in others.

>>>>

\section{Discussion}
\label{sec:discussion}
%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, Eve Kovacs, Tony Tyson, Tina Peters)
In this paper we presented results evaluating the computation of individual galaxy photometric redshift PDFs for twelve photo-$z$ codes.  As discussed in Section~\ref{sec:metrics} each $p(z)$ should accurately reflect the relative likelihood as a function of redshift for each galaxy in an informative way; that is, the estimates should provide useful information per individual galaxy, not just the ensemble.  All codes were provided a set of representative training data and tested on an idealized set of model galaxies with high signal-to-noise and photometry with no confounding effects due to blending, instrumental effects, the night sky, or other complications included.  The goal was not to determine a ``best'' photo-$z$ code: in many ways, this was a baseline test of a ``best case scenario'' to predict the expected photo-$z$ performance if a stage IV dark energy survey was to obtain complete training samples and perfectly calibrated their multi-band photometry.  Given these idealized conditions, any deficiencies observed in a photo-$z$ code's performance should be a cause for concern, and may be evidence of a problem with either/both of the specific code implementation or the underlying algorithm.  In order to meet the stringent LSST goals for photo-$z$ performance, identifying and correcting such problems is an important first step before tackling more realistic data in future challenges, and codes that do not perform well may not be worth pursuing in future challenges.  Many of the codes tested performed well; however, several did not meet the stringent goals that have been laid out for LSST photometric redshift performance for individual galaxies, as laid out in the LSST SRD (See Section~\ref{sec:intro}.  This is a cause for concern, given the idealized conditions, and the individual code responses will be studied in detail moving forward.  If methods can not reach the goals on idealized data, then they will almost surely not meet those same goals when the more complex problems that we expect to arise from real LSST data are included.  The results presented in this paper enable an evaluation of which algorithms are the most promising moving forward, and potentially point to implementation choices or mistakes which could be improved or corrected in others.
